Reasoning about a Capability Machine with Local Capabilities

### 2017-06-21 popl-2018/paper.tex
small part about single stack, please read

>>>>

\emph{Single stack} A single stack is a good choice for the simple capability
machine presented here, because it works well with higher-order functions. The
alternative to a single stack would be to have one stack per component. With
multiple stacks on this simple capability machine, it is not entirely obvious
how each component would retrieve their stack pointer. Further with higher-order
functions, it is not clear which stack the higher-order function should
use. Should it use the stack of the component that created it or the stack of
the component in which it is called. If we let it use the stack of the component
that uses the higher-order function, then what is the purpose of having multiple
stacks when the stack is not exclusive to each component. If we let it use the
stack of its creator, then the question is how do you obtain this stack
pointer. We do not claim that it is impossible to make it work with multiple
stack in the context of higher-order functions, but it is not obvious how it
would work.
